---
title: "Indexed DB Write-Only (one-shot) Transactions"
output:
  html_document:
    toc: true
    theme: flatly
    smart: true
    self_contained: false
---

This is an experiment to evaluate the benefit of immediately committing a
transaction once it's task queue is empty. Normally the browser process waits
for all requests to be completed (i.e. onsuccess/onabort) to be called, and
the Render process calls back to the browser to complete the transaction once
all outstanding requests are completed.

Performance metrics for https://crbug.com/496327.

The current version which waits for request completion. Here are the times
for repeated calls to IDBObjectStore.put with varying value sizes:

```{r, echo=FALSE}
library(pander)
```

This is how it functions today (stable)

```{r}
(standard = read.csv("idb-write-standard.csv", header=TRUE, row.names=1))
```

And with the experimental `{immediateCommit:true}` option when creating a transaction.

```{r, echo=TRUE}
(modified = read.csv("idb-write-modified.csv", header=TRUE, row.names=1))
```

So the performance improvements in the given experiments are:

```{r}
(speedup = standard / modified)
```
And plotting them:

```{r, echo=TRUE}
iterations <- colnames(speedup)
markers <- 1:8
colors <- c("darkgreen", "blue", "brown", "magenta")
matplot(speedup, type="l", col=colors, bty="n", pch=markers, xlab="Iterations")
legend("topleft", col=colors, iterations, bg="white", lwd=1, pch=markers)
```
